The Exoplanet Orbit Database \textsc{II}: Updates to exoplanets.org

### 2014-07-22 draft/ms.tex
Typo fixes in abstract

The Exoplanet Orbit Database (EOD) compiles orbital, transit, host
star, and other parameters of robustly detected exoplanets reported in
the peer-reviewed literature. The EOD can be navigated through the
Exoplanet Data Explorer (EDE) Plotter and Table, available on the
World Wide Web at exoplanets.org. The EOD contains data for 1492
confirmed exoplanets as of July 2014.  The EOD descends from a table
in \citet{Butler2002} and the Catalog of Nearby Exoplanets
\citep{Butler2006}, and the first complete documentation for the EOD
and the EDE was presented in \cite{Wright2011}. In this work, we
describe our work since then.  We have expanded the scope of the EOD
to include secondary eclipse parameters, asymmetric uncertainties, and
expanded the EDE to include the sample of over 3000 \kepler\ Objects
of Interest (KOIs), and other real planets without good orbital
parameters (such as many of those those detected by microlensing and
imaging.) Users can download the latest version of the entire EOD as a
single comma separated value file from the front page of
exoplanets.org.

>>>>

The Exoplanet Orbit Database (EOD) compiles orbital, transit, host
star, and other parameters of robustly detected exoplanets reported in
the peer-reviewed literature. The EOD can be navigated through the
Exoplanet Data Explorer (EDE) Plotter and Table, available on the
World Wide Web at exoplanets.org. The EOD contains data for 1492
confirmed exoplanets as of July 2014.  The EOD descends from a table
in \citet{Butler2002} and the Catalog of Nearby Exoplanets
\citep{Butler2006}, and the first complete documentation for the EOD
and the EDE was presented in \cite{Wright2011}. In this work, we
describe our work since then.  We have expanded the scope of the EOD
to include secondary eclipse parameters, asymmetric uncertainties, and
expanded the EDE to include the sample of over 3000 \kepler\ Objects
of Interest (KOIs), and other real planets without good orbital
parameters (such as many of those detected by microlensing and
imaging). Users can download the latest version of the entire EOD as a
single comma separated value file from the front page of
exoplanets.org.
